\section{Future Scope}
This project was an enriching experience for us, amidst all the challenges it presented. We definitely see quite a few ways in which this project can live on, as detailed in the following sections:

\subsection{Expansion of Supported Grammar}
From here, we could explore an expansion of supported grammar, to include constructs such as sequences and arrays. We also came up with an extended version of the ANTLR4 g4 file for OCaml, which will be helpful in kickstarting this process. In order to do so, it may also be worthwhile updating the frontend to a more source academy-like setup that allows for both evaluation of single line expressions and multi-line input.
  
\subsection{Evaluation and Execution}
The next step for statically type checked code is evaluation and actual execution. Collaboration with other groups that may have worked on that step of the process could be an exciting way to move forward. In doing so, elements of each project may have to be updated as well in the interest of compatibility and efficiency. One example would be studying if Listeners or Visitors would be most appropriate for handling the intended use cases. In the context of a complete system, optimal use of the call stack and heap will need to be considered. In the process of researching about this project, we came across a compiler called js-of-ocaml, which could be employed as well. On the github repository, it is described as a compiler from OCaml bytecode to JavaScript that makes it possible to run pure OCaml programs in JavaScript environment like browsers and Node.js.
